Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-31 ms.tex
more updates to table.
Lx caption

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average (unresolved) nuclear X-ray luminosity $\langle L_X \rangle = \epsilon_X \Mdot c^2$ as a function of SMBH mass, predicted from our models for the average star formation history (Fig.~\ref{fig:bh_growth}; {\it black line}) calculated for the average Nuker power-law index $\Gamma(M_{\bullet})$ derived from the galaxy sample of \citet{LauerFaber+:2007a}.  Shown for comparison are the measurements $L_X/L_{\rm edd}$ values (red stars) and
  upper limits (red triangles) from the \citet{Miller+15} sample of early-type galaxies, with a green line showing the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$.  The left panel shows the case of a constant radiative efficiency $\epsilon_X=10^{-4}$, while the right hand panel shows an efficiency $\epsilon_X=
  \left(\frac{\epsilon_{\rm bol}}{0.1}\right)\frac{\Mdot}{\MdotEdd}$ predicted by some models for radiatively inefficient accretion.  Also shown for comparison are the X-ray luminosities calculated using the maximum thermally-stable accretion rate ({\it orange line}), SN Ia-regulated accretion rate, and Compton-regulated accretion rate ({\it pink line}),  again calculated for the average star formation history.}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.  Black lines show our prediction in the case of heating due to the average star formation history for galaxies corresponding to each black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the relationship  $\Gamma(M_{\bullet})$ derived from the \citet{LauerFaber+:2007a} sample.  Shown for comparison are the measurements ({\it red stars}) and
  upper limits ({\it red triangles}) for $L_X/L_{\rm edd}$ values, from the \citet{Miller+15} sample of early-type galaxies (a green line shows the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is calculated assuming a constant radiative efficiency $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand panel assumes $\epsilon_X=
  (\epsilon_{\rm bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g., \citealt{Narayan&Yi95}).  Shown for comparison are the X-ray luminosities calculated for the maximum thermally-stable accretion rate ({\it orange line}; eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion rate  ({\it pink line}; eq.~[\ref{eq:MdotCa}]),  again all calculated for the average star formation history corresponding to each SMBH mass.}
\end{figure*}
